---
title: "Syed_stocks"
author: "Syed"
date: "2/24/2020"
output: html_document
---

# Syed
# key = 34a99316
# av_key = 8O2HOV0F5K39AXOJ

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# To check Log Syed using the key obtained.

```{r}

log <- "https://www.projectrex.net/stocks/?key=34a99316&av_key=8O2HOV0F5K39AXOJ&request=log"
log.syed <- as.data.frame(fromJSON(log))
view(log.syed)

```

# To pull the profile table and assign the counter column to be zero and the budget to be zero.

```{r}
profile <- "https://www.projectrex.net/stocks/?key=34a99316&av_key=8O2HOV0F5K39AXOJ&request=profile"
profileFull <- fromJSON(profile)
profile.syed <- profileFull$shares
profile.syed$counter = 0
profile.syed
BUDGET <- 0

# To set the budget above the maximum price of share owned.
max_price <- max(profile.syed$price)
max_price

# To define the vector of symbols to trade with
stocks.s <- c("F", "JNJ","NUGT","AAPL", "SPCE", "INST", "TRQ","PVH", "MSFT", "DELL", "BAS", "NFLX", "NUGT", "JCP",  "UA","V", "INST")
```

# To specify the script to run in a while loop for almost 6 hours

```{r}
end_time <- Sys.time() + 20000

# To specify alphavantage key for pulling the ema.
av_api_key("8O2HOV0F5K39AXOJ")
```

# To execute the model for the next 6 hours with a while loop iterating through the above defined vector of stock symbols

```{r}

while (Sys.time() <= end_time) {
  
  SLEEP <- seq(from = 0, to = 10, by = 2)
  x=1
  for (i in stocks.s) {
    ema.30.open.2 = as.data.frame(av_get(symbol = i,
                                       av_fun = "EMA",
                                       interval = "5min",
                                       time_period = 30,
                                       series_type = "open"))
    ema.100.open.2 = as.data.frame(av_get(symbol = i,
                                        av_fun = "EMA",
                                        interval = "5min",
                                        time_period = 100,
                                        series_type = "open"))

    # To check for the cross over of 30 day ema with the 100 day ema
    
    EMA_POINT <- ema.30.open$ema[[1]] - ema.100.open$ema[[1]]
    
if( EMA_POINT >= 0 && profile.syed$counter [profile.syed$symbol == i] <=30 ) {
# Sell if the short term ema is leading 
  if (profile.syed$quantity[profile.syed$symbol == i] > 1 && profile.syed$counter [profile.syed$symbol == i] <=30) {
    Transaction <- fromJSON(sell <- paste("https://www.projectrex.net/stocks/?key=34a99316&av_key=8O2HOV0F5K39AXOJ&request=sell&quantity=1&symbol=",i, sep = ""))
    # Update Profile
    profile.syed$quantity[profile.syed$symbol == i] <- profile.syed$quantity[profile.syed$symbol == i] - 1
    profile.syed$counter[profile.syed$symbol == i] <- profile.syed$counter[profile.syed$symbol == i] + 1
    # Update Budget
    BUDGET <- BUDGET + Transaction$price
  }
  
 
} else if(BUDGET > max_price && profile.syed$counter [profile.syed$symbol == i] <=30 ) {
  # Buy if the long term ema is leading
  Transaction <- fromJSON(buy <- paste("https://www.projectrex.net/stocks/?key=34a99316&av_key=8O2HOV0F5K39AXOJ&request=buy&quantity=1&symbol=",i, sep = ""))
  # Update Profile
  profile.syed$quantity[profile.syed$symbol == i] <- profile.syed$quantity[profile.syed$symbol == i] + 1
  profile.syed$counter[profile.syed$symbol == i] <- profile.syed$counter[profile.syed$symbol == i] + 1
  # Update Budget
  BUDGET <- BUDGET - Transaction$price 
}
    # To put the loop in a sleep for a minute to avoid exceeding the allowed api calls per minute.
    
if (x %in% SLEEP){
  Sys.sleep(60)
}  
x <- x+1
  }
}

```

# Zimin 
# key = 31a7d251
# av_key = S06YJS8V8LH7G0BH


```{r}
#Zimin log
log.z <- "https://www.projectrex.net/stocks/?key=31a7d251&av_key=S06YJS8V8LH7G0BH&request=log"

log.zimin <- fromJSON(log.z)
z.log <- as.data.frame(log.zimin$log)
View(z.log)
```


# To pull the profile table and assign the counter column to be zero and the budget to be zero.

```{r}
profile <- "https://www.projectrex.net/stocks/?key=31a7d251&av_key=S06YJS8V8LH7G0BH&request=profile"
profileFull <- fromJSON(profile)
profile.zimin <- profileFull$shares
profile.zimin$counter = 0
profile.zimin
BUDGET <- 0

# To set the budget above the maximum price of share owned.
max_price <- max(profile.zimin$price)
max_price

# To define the vector of symbols to trade with
stocks.s <- c("F", "JNJ","NUGT","AAPL", "SPCE", "INST", "TRQ","PVH", "MSFT", "DELL", "BAS", "NFLX", "NUGT", "JCP",  "UA","V", "INST")
```

# To specify the script to run in a while loop for almost 6 hours

```{r}
end_time <- Sys.time() + 20000

# To specify alphavantage key for pulling the ema.
av_api_key("8O2HOV0F5K39AXOJ")
```

# To execute the model for the next 6 hours with a while loop iterating through the above defined vector of stock symbols

```{r}

while (Sys.time() <= end_time) {
  
  SLEEP <- seq(from = 0, to = 10, by = 2)
  x=1
  for (i in stocks.s) {
    ema.30.open.2 = as.data.frame(av_get(symbol = i,
                                       av_fun = "EMA",
                                       interval = "5min",
                                       time_period = 30,
                                       series_type = "open"))
    ema.100.open.2 = as.data.frame(av_get(symbol = i,
                                        av_fun = "EMA",
                                        interval = "5min",
                                        time_period = 100,
                                        series_type = "open"))

    # To check for the cross over of 30 day ema with the 100 day ema
    
    EMA_POINT <- ema.30.open$ema[[1]] - ema.100.open$ema[[1]]
    
if( EMA_POINT >= 0 && profile.zimin$counter [profile.zimin$symbol == i] <=30 ) {
# Sell if the short term ema is leading 
  if (profile.zimin$quantity[profile.zimin$symbol == i] > 1 && profile.zimin$counter [profile.zimin$symbol == i] <=30) {
    Transaction <- fromJSON(sell <- paste("https://www.projectrex.net/stocks/?key=31a7d251&av_key=S06YJS8V8LH7G0BH&request=sell&quantity=1&symbol=",i, sep = ""))
    # Update Profile
    profile.zimin$quantity[profile.zimin$symbol == i] <- profile.zimin$quantity[profile.zimin$symbol == i] - 1
    profile.zimin$counter[profile.zimin$symbol == i] <- profile.zimin$counter[profile.zimin$symbol == i] + 1
    # Update Budget
    BUDGET <- BUDGET + Transaction$price
  }
  
 
} else if(BUDGET > max_price && profile.zimin$counter [profile.zimin$symbol == i] <=30 ) {
  # Buy if the long term ema is leading
  Transaction <- fromJSON(buy <- paste("https://www.projectrex.net/stocks/?key=31a7d251&av_key=S06YJS8V8LH7G0BH&request=buy&quantity=1&symbol=",i, sep = ""))
  # Update Profile
  profile.zimin$quantity[profile.zimin$symbol == i] <- profile.zimin$quantity[profile.zimin$symbol == i] + 1
  profile.zimin$counter[profile.zimin$symbol == i] <- profile.zimin$counter[profile.zimin$symbol == i] + 1
  # Update Budget
  BUDGET <- BUDGET - Transaction$price 
}
    # To put the loop in a sleep for a minute to avoid exceeding the allowed api calls per minute.
    
if (x %in% SLEEP){
  Sys.sleep(60)
}  
x <- x+1
  }
}

```

